---
title: 'The treatment of error in learners of Russian as a foreign language: visual
  analytics'
author: 'Wenceslao Arroyo-Machado'
date: '`r Sys.Date()`'
output:
  html_document:
    css: style.css
    toc: yes
    toc_float: yes
    number_sections: yes
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r packages, warning=FALSE, message=FALSE}
library(testnet)
library(cluster)
library(fmsb)
library(dplyr)
library(GGally) 
library(scales)
library(wesanderson)
```

# Data

```{r import_data}
answers <- read.delim('data/answers.tsv',
                      stringsAsFactors = FALSE, check.names = FALSE)

categories <- read.delim('data/tags.tsv',
                         header = TRUE,
                         colClasses = c('character'),
                         stringsAsFactors = FALSE, check.names = FALSE)

c_answers <- read.delim('data/correct_ans.tsv',
                        header = TRUE,
                        colClasses = c('character'),
                        stringsAsFactors = FALSE, check.names = FALSE)
```

# Analysis
## Linguistic level
Self-perceived linguistic level boxplot is generated before filtering the dataset to only answers.

```{r language}
ggplot(data=answers, aes(x=`¿Qué nivel crees que refleja mejor tu dominio de la lengua rusa en términos generales?`, y=Puntuación/75))+
  geom_boxplot(fill='#2297e6', alpha=0.7)+
  geom_jitter(width = 0.2, height = 0)+
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0.4, 1))+
  labs(x='Self-perceived linguistic level', y='Score (%)')+
  theme_minimal()+
  theme(axis.title = element_text(size=14),
        axis.text = element_text(size=12),
        legend.position = 'bottom',
        legend.key.width = unit(1, 'cm'),
        legend.title = element_text(vjust = 0.85))
```

## Co-error network
From the answers, co-error networks are generated, one with all the relations and another with the edge weights greater than 1.

```{r error_network, warning=FALSE, message=FALSE}
answers <- answers[,c(11:85)]
edges <- obtain_edges(answers, c_answers)

cofails <- inner_join(x = edges, y = edges, by = 'source')
cofails <- cofails[which(!(cofails$target.x == cofails$target.y)),]
cofails <- mutate(cofails, Source = pmin(target.x, 
                                                target.y), Target = pmax(target.x, target.y))
cofails <- cofails[, which(!(names(cofails) %in% c('target.x', 
                                                   'target.y', 'weight.x', 'weight.y')))]
cofails <- distinct(cofails, .keep_all = TRUE)
names(cofails)[names(cofails) == 'source'] <- 'Weight'
cofails$Weight <- 1
cofails <- group_by(cofails, Source, Target)
cofails <- summarise(cofails, Weight = sum(Weight))
cofails <- as.data.frame(cofails, stringsAsFactors = FALSE)

write.table(cofails, 'map/fails_map.csv', sep = ',', row.names = FALSE, col.names = FALSE)
write.table(cofails[which(cofails$Weight>1),], 'map/fails_map_filter.csv', sep = ',', row.names = FALSE, col.names = FALSE)
```

## Categories profiles
Student error profiles by category are calculated.

```{r profiles, warning=FALSE, message=FALSE}
for(i in c(1:dim(c_answers)[1])){
  c_answers[i,1] <- strsplit(c_answers[i,1], '\\.')[[1]][1]
  categories[i,1] <- strsplit(categories[i,1], '\\.')[[1]][1]
}

edges <- inner_join(edges, categories[,c(1,2)], by=c('target'='Preguntas'))

profiles <- edges[,c('source', 'weight', 'Categorías')] %>%
  group_by(source, Categorías) %>%
  summarise(weight=sum(weight))
```

Student error rates are calculated for each of the categories.

```{r categories}
a <- xtabs(weight~source+Categorías, profiles)
a <- as.data.frame(matrix(a, ncol = ncol(a), dimnames = dimnames(a)))
a$total <- rowSums(a)

a_p <- a
a_p[,1] <- a_p[,1]/a_p[,6]
a_p[,2] <- a_p[,2]/a_p[,6]
a_p[,3] <- a_p[,3]/a_p[,6]
a_p[,4] <- a_p[,4]/a_p[,6]
a_p[,5] <- a_p[,5]/a_p[,6]
```

From the profiles is obtained the coordinate and boxplot graphs.

```{r ggcoord_categories, warning=FALSE}
ggparcoord(data = a_p,
           columns = 1:5, boxplot = TRUE,
           groupColumn = 'total', showPoints = TRUE,
           scale = 'globalminmax') +
  scale_y_continuous(labels = percent_format(accuracy = 1))+
  scale_colour_gradientn(colors=wes_palette('Zissou1', n = 5), name='Total failures', breaks=extended_breaks())+
  labs(x='Categories', y='Percentage of failures')+
  theme_minimal()+
  theme(axis.title = element_text(size=14),
        axis.text = element_text(size=12),
        legend.position = 'bottom',
        legend.key.width = unit(1, 'cm'),
        legend.title = element_text(vjust = 0.85))
```

## Cluster profiles
From the error percentiles, clusters of errors are obtained using kmeans.

```{r}
a_clusters <- a_p

a_clusters[,1] <- 100*percent_rank(a_clusters[,1])
a_clusters[,2] <- 100*percent_rank(a_clusters[,2])
a_clusters[,3] <- 100*percent_rank(a_clusters[,3])
a_clusters[,4] <- 100*percent_rank(a_clusters[,4])
a_clusters[,5] <- 100*percent_rank(a_clusters[,5])

k2 <- kmeans(a_clusters[,1:5], centers = 4, nstart = 25, iter.max = 100)

a_clusters$clusters <- k2$cluster
a_clusters_2 <- a_clusters %>%
  group_by(clusters) %>%
  summarise_all(.funs = mean)

max_min <- data.frame(
  aspecto = c(100, 0), caso = c(100, 0), lex = c(100, 0),
  `o.com ` = c(100, 0), v.mov = c(100, 0), check.names = F
)

rownames(max_min) <- c('Max', 'Min')

a_clusters_2 <- rbind.data.frame(as.data.frame(a_clusters_2[,2:6]), max_min)
```

The clusters are presented as radar plots.

```{r}
radarchart(a_clusters_2[c('Max', 'Min', '1'),], pcol='#00AFBB', pfcol = alpha('#00AFBB', 0.5))
radarchart(a_clusters_2[c('Max', 'Min', '2'),], pcol='#E7B800', pfcol = alpha('#E7B800', 0.5))
radarchart(a_clusters_2[c('Max', 'Min', '3'),], pcol='#FC4E07', pfcol = alpha('#FC4E07', 0.5))
radarchart(a_clusters_2[c('Max', 'Min', '4'),], pcol='#046C9A', pfcol = alpha('#046C9A', 0.5))
```

## Subcategories profiles
The same analysis is carried out but at subcategory level.

```{r sub_profiles, warning=FALSE, message=FALSE}
edges <- obtain_edges(answers, c_answers)
edges <- inner_join(edges, categories[,c(1,3)], by=c('target'='Preguntas'))
names(edges)[4] <- 'Categorías'

profiles <- edges[,c('source', 'weight', 'Categorías')] %>%
  group_by(source, Categorías) %>%
  summarise(weight=sum(weight))

a <- xtabs(weight~source+Categorías, profiles)
a <- as.data.frame(matrix(a, ncol = ncol(a), dimnames = dimnames(a)))
a$total <- rowSums(a)

a_p <- a

a_p[,1] <- a_p[,1]/a_p[,10]
a_p[,2] <- a_p[,2]/a_p[,10]
a_p[,3] <- a_p[,3]/a_p[,10]
a_p[,4] <- a_p[,4]/a_p[,10]
a_p[,5] <- a_p[,5]/a_p[,10]
a_p[,6] <- a_p[,6]/a_p[,10]
a_p[,7] <- a_p[,7]/a_p[,10]
a_p[,8] <- a_p[,8]/a_p[,10]
a_p[,9] <- a_p[,9]/a_p[,10]
```

From the profiles (subcategories) is obtained the coordinate and boxplot graphs.

```{r ggcoord_subcategories, warning=FALSE}
ggparcoord(data = a_p,
           columns = 1:9, boxplot = TRUE,
           groupColumn = 'total', showPoints = TRUE,
           scale = 'globalminmax') +
  scale_y_continuous(labels = percent_format(accuracy = 1))+
  scale_colour_gradientn(colors=wes_palette('Zissou1', n = 5), name='Total failures', breaks=extended_breaks())+
  labs(x='Subategories', y='Percentage of failures')+
  theme_minimal()+
  theme(axis.title = element_text(size=14),
        axis.text = element_text(size=12),
        legend.position = 'bottom',
        legend.key.width = unit(1, 'cm'),
        legend.title = element_text(vjust = 0.85))
```